---
title: "Forecasting Competition Challenges"
author: "Lingyue Hao, Seohyun Oh"
date: "`r Sys.Date()`"
output: pdf_document

---

# Github Repo 
https://github.com/lingyuehao/Oh_Hao_ENV797_TSA_ForecastCompetition_S26

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
```

```{r}
library(readxl)
library(dplyr)
library(tidyr)
library(lubridate)
library(stringr)
library(forecast)
library(ggplot2)
```

# Load Data

```{r}
load_raw <- read_excel("data/load.xlsx")
temp_raw <- read_excel("data/temperature.xlsx")
rh_raw   <- read_excel("data/relative_humidity.xlsx")
sub_template <- read.csv("output/submission_template.csv")
```

```{r}
glimpse(load_raw)
glimpse(temp_raw)
glimpse(rh_raw)
```

```{r}
names(load_raw)
names(temp_raw)
names(rh_raw)

head(load_raw)
head(temp_raw)
head(rh_raw)

```

```{r}
tail(load_raw$date)
tail(temp_raw$date)
tail(rh_raw$date)
```

# Data Preprocessing

```{r}
## transfer load to daily
load_daily <- load_raw %>%
  mutate(date = as.Date(date)) %>%
  mutate(
    load_daily = rowMeans(select(., starts_with("h")), na.rm = TRUE)
  ) %>%
  select(date, load_daily)
```

```{r}
## transfer temp to daily
temp_daily <- temp_raw %>%
  mutate(date = as.Date(date)) %>%
  mutate(
    temp_hourly_avg = rowMeans(select(., starts_with("t_ws")), na.rm = TRUE)
  ) %>%
  group_by(date) %>%
  summarise(
    temp_daily = mean(temp_hourly_avg, na.rm = TRUE),
    .groups = "drop"
  )
```

```{r}
## transfer humidity to daily
rh_daily <- rh_raw %>%
  mutate(date = as.Date(date)) %>%
  mutate(
    rh_hourly_avg = rowMeans(select(., starts_with("rh_ws")), na.rm = TRUE)
  ) %>%
  group_by(date) %>%
  summarise(
    rh_daily = mean(rh_hourly_avg, na.rm = TRUE),
    .groups = "drop"
  )
```

```{r}
## combine daily data
daily_data <- load_daily %>%
  left_join(temp_daily, by = "date") %>%
  left_join(rh_daily, by = "date")

glimpse(daily_data)
head(daily_data)
summary(daily_data)
colSums(is.na(daily_data))
```

```{r}
# load 
daily_load <- daily_data %>% 
  select(date, load_daily)

# load + temp 
daily_load_temp <- daily_data %>% 
  select(date, load_daily, temp_daily)

glimpse(daily_load_temp)
```

# Train/Validation split

```{r}
# split train and validation data (load + temp + humid)
 train_data <- daily_data %>%
  filter(date <= as.Date("2010-06-30"))

valid_data <- daily_data %>%
  filter(date >= as.Date("2010-07-01") &
         date <= as.Date("2010-07-31"))

# split train and validation data (load)
 train_data_load <- daily_load %>%
  filter(date <= as.Date("2010-06-30"))

valid_data_load <- daily_load %>%
  filter(date >= as.Date("2010-07-01") &
         date <= as.Date("2010-07-31"))

# split train and validation data (load + temp)
 train_data_load_temp <- daily_load_temp %>%
  filter(date <= as.Date("2010-06-30"))

valid_data_load_temp <- daily_load_temp %>%
  filter(date >= as.Date("2010-07-01") &
         date <= as.Date("2010-07-31"))

# use all available historical data up to 2011-06-30
full_data <- daily_data %>%
  filter(date >= as.Date("2005-01-01"),
         date <= as.Date("2011-06-30")) %>%
  arrange(date)

full_data_load <- daily_load %>%
  filter(date >= as.Date("2005-01-01"),
         date <= as.Date("2011-06-30")) %>%
  arrange(date)

full_data_load_temp <- daily_load_temp %>%
  filter(date >= as.Date("2005-01-01"),
         date <= as.Date("2011-06-30")) %>%
  arrange(date)
```

```{r}
# create time series with weekly seasonality
train_ts <- ts(train_data$load_daily, frequency = 7)
train_msts <- msts(train_data$load_daily, seasonal.periods = c(7, 365)) 

train_ts_load <- ts(train_data_load$load_daily, frequency = 7)
train_msts_load <- msts(train_data_load$load_daily, seasonal.periods = c(7, 365)) 

train_ts_load_temp <- ts(train_data_load_temp$load_daily, frequency = 7)
train_msts_load_temp <- msts(train_data_load_temp$load_daily, seasonal.periods = c(7, 365)) 

# create time series with weekly seasonality
full_ts <- ts(full_data$load_daily, frequency = 7)
full_msts <- msts(full_data$load_daily, seasonal.periods = c(7, 365)) 

full_ts_load <- ts(full_data_load$load_daily, frequency = 7)
full_msts_load <- msts(full_data_load$load_daily, seasonal.periods = c(7, 365)) 

full_ts_load_temp <- ts(full_data_load_temp$load_daily, frequency = 7)
full_msts_load_temp <- msts(full_data_load_temp$load_daily, seasonal.periods = c(7, 365)) 
```

# EDA

```{r}
ggplot(daily_load, aes(x = date, y = load_daily)) +
  geom_line() +
  labs(title = "Daily Load Over Time", x = "Date", y = "Daily Load") +
  theme_minimal()
```

> strong seasonality in weekly, yearly (reason for using msts)

```{r}
ggAcf(train_data_load$load_daily)
ggPacf(train_data_load$load_daily)
```

> strong non-stationarity, low-order AR process

```{r}
fit_mstl <- mstl(train_msts_load)
autoplot(fit_mstl)
```

> Trend exists(non-stationary), weak weekly seasonality, strong yearly seasonality

```{r}
daily_load %>%
  mutate(weekday = wday(date, label = TRUE)) %>%
  ggplot(aes(x = weekday, y = load_daily)) +
  geom_boxplot() +
  labs(title = "Load by Weekday", x = "Weekday", y = "Daily Load") +
  theme_minimal()
```

# Modeling

Among the models evaluated, the ETS model with mean bias correction achieved the best performance on Kaggle, with a score of 0.0928. 

Ensemble models combining ETS and TBATS followed, with scores around 0.10, indicating that while ensembling provided some improvements, the bias-corrected ETS model remained the most effective.

For implementation, ETS was trained using a weekly seasonal structure (`ts` with frequency = 7), as it yielded comparable performance to multi-seasonal formulations. In contrast, TBATS was implemented using `msts` to capture multiple seasonal components in the data.

```{r, include=FALSE}
## Baseline Model(ETS, TBATS)

## ETS 

# ETS Model Training 
fit_ets <- ets(train_ts)
fc_ets <- forecast(fit_ets, h = nrow(valid_data))

# accuracy
accuracy(fc_ets, valid_data$load_daily)

# plot actual vs forecast on validation dates
validation_results <- data.frame(
  date = valid_data$date,
  actual = valid_data$load_daily,
  forecast = as.numeric(fc_ets$mean)
)

ggplot(validation_results, aes(x = date)) +
  geom_line(aes(y = actual, color = "Actual"), linewidth = 1) +
  geom_line(aes(y = forecast, color = "ETS"), linewidth = 1) +
  labs(
    title = "ETS: Validation Forecast vs Actual",
    x = "Date",
    y = "Daily Load",
    color = ""
  ) +
  theme_minimal()
```

```{r, include=FALSE}

# ETS Model Forecast 
final_ets <- ets(full_ts)
final_fc <- forecast(final_ets, h = nrow(sub_template))

# create final submission file
submission <- sub_template %>%
  mutate(load = as.numeric(final_fc$mean))

# save csv
write.csv(submission, "output/submission_ets.csv", row.names = FALSE)
```

```{r, include=FALSE}
# TBATS Model Training  
fit_tbats <- tbats(train_msts)
fc_tbats <- forecast(fit_tbats, h = nrow(valid_data))

# accuracy
ac_tbats <- accuracy(fc_tbats, valid_data$load_daily)

# plot actual vs forecast on validation dates
validation_results_tbats <- data.frame(
  date = valid_data$date,
  actual = valid_data$load_daily,
  forecast = as.numeric(fc_tbats$mean)
)

ggplot(validation_results_tbats, aes(x = date)) +
  geom_line(aes(y = actual, color = "Actual"), linewidth = 1) +
  geom_line(aes(y = forecast, color = "TBATS"), linewidth = 1) +
  labs(
    title = "TBATS: Validation Forecast vs Actual",
    x = "Date",
    y = "Daily Load",
    color = ""
  ) +
  theme_minimal()

print(ac_tbats)
```

```{r, include=FALSE}
# TBATS Model Forecast  
final_tbats_fit <- tbats(full_msts)
final_tbats_fc <- forecast(final_tbats_fit, h = nrow(sub_template))

# create final submission file
submission_tbats <- sub_template %>%
  mutate(load = as.numeric(final_tbats_fc$mean))

# save csv
write.csv(submission_tbats, "output/submission_tbats.csv", row.names = FALSE)
```

## Model 1: ETS with Bias Correction

This model applies mean bias correction to the ETS forecast, which improves accuracy by correcting systematic underestimation observed in the validation set.

```{r}
# ETS with Validation-based Bias Correction 
#  Refit ETS on training set to evaluate bias on validation
fit_ets_R <- ets(train_ts)
fc_ets_R  <- forecast(fit_ets_R, h = nrow(valid_data))

# Compute mean systematic bias (actual - forecast) on validation
residuals_valid <- valid_data$load_daily - as.numeric(fc_ets_R$mean)
mean_bias   <- mean(residuals_valid)
median_bias <- median(residuals_valid)
mean_fc     <- mean(fc_ets_R$mean)

cat("Mean bias on validation:", round(mean_bias, 4), "\n")
cat("Median bias on validation:", round(median_bias, 4), "\n")
cat("Mean forecast value:", round(mean_fc, 4), "\n")
cat("Relative mean bias (%):", round(mean_bias / mean_fc * 100, 2), "%\n")

#   Generate final forecast and apply mean bias correction
fit_ets_final <- ets(full_ts)
fc_ets_final  <- forecast(fit_ets_final, h = nrow(sub_template))

# Apply additive mean bias correction
submission_ets_biascorr <- sub_template %>%
  mutate(load = as.numeric(fc_ets_final$mean) + mean_bias)

write.csv(submission_ets_biascorr, "output/submission_ets_biascorr.csv", row.names = FALSE)

# Preview
head(submission_ets_biascorr)
```

## Model 2: ETS with Median Bias Correction

This model uses median bias correction, providing a more robust adjustment against extreme residual values compared to mean correction.

```{r}
#  ETS with Median Bias Correction  

submission_ets_median_bias <- sub_template %>%
  mutate(load = as.numeric(fc_ets_final$mean) + median_bias)

write.csv(submission_ets_median_bias, 
          "output/submission_ets_median_bias.csv", row.names = FALSE)

cat("Median bias used:", round(median_bias, 4), "\n")
cat("Mean bias was:   ", round(mean_bias, 4), "\n")
cat("Difference:      ", round(median_bias - mean_bias, 4), "\n")

head(submission_ets_median_bias)
```

## Model 3: Ensemble: 75% ETS + 25% TBATS

This ensemble combines 75% ETS and 25% TBATS forecasts, placing greater emphasis on ETS while incorporating multi-seasonal information from TBATS.

```{r, eval=FALSE, include=FALSE}
# Fine-grained weight search for ETS + TBATS 
sub_ets   <- read.csv("output/submission_ets.csv")
sub_tbats <- read.csv("output/submission_tbats.csv")

weights_to_try <- c(0.60, 0.65, 0.75, 0.80, 0.85)

for (w_ets in weights_to_try) {
  w_tbats <- 1 - w_ets
  sub_tmp <- sub_template %>%
    mutate(load = w_ets * sub_ets$load + w_tbats * sub_tbats$load)
  
  fname <- sprintf("submission_ens_ets%02d_tbats%02d.csv",
                   round(w_ets * 100), round(w_tbats * 100))
  write.csv(sub_tmp, fname, row.names = FALSE)
  cat("Saved:", fname, "\n")
}
```

```{r}
# Ensemble (75/25)
sub_ets   <- read.csv("output/submission_ets.csv")
sub_tbats <- read.csv("output/submission_tbats.csv")

submission_ens_ets75_tbats25 <- sub_template %>%
  mutate(load = 0.75 * sub_ets$load + 0.25 * sub_tbats$load)

write.csv(submission_ens_ets75_tbats25,
          "output/submission_ens_ets75_tbats25.csv",
          row.names = FALSE)
```

## Model 4: Ensemble: 70% ETS + 30% TBATS

This ensemble uses a 70/30 weighting between ETS and TBATS, slightly increasing the contribution of TBATS to better capture multiple seasonal patterns.

```{r}
# ETS-heavy Weighted Ensemble 
sub_ets   <- read.csv("output/submission_ets.csv")
sub_tbats <- read.csv("output/submission_tbats.csv")

 
submission_ens_ets_heavy <- sub_template %>%
  mutate(load = 0.7 * sub_ets$load + 0.3 * sub_tbats$load)

write.csv(submission_ens_ets_heavy,
          "output/submission_ens_ets_heavy.csv", row.names = FALSE)
```

## Model 5: Ensemble: 65% ETS + 35% TBATS

This ensemble further increases the TBATS contribution (65/35), allowing more flexibility in modeling complex seasonal structures.

```{r}
# Ensemble (65/35)
submission_ens_ets65_tbats35 <- sub_template %>%
  mutate(load = 0.65 * sub_ets$load + 0.35 * sub_tbats$load)

write.csv(submission_ens_ets65_tbats35,
          "output/submission_ens_ets65_tbats35.csv",
          row.names = FALSE)
```


```{r, eval=FALSE, include=FALSE}
# ETS with Trimmed Mean Bias Correction  
# Compute trimmed mean (drop 10% from each tail)
trimmed_bias_10 <- mean(residuals_valid, trim = 0.10)
trimmed_bias_20 <- mean(residuals_valid, trim = 0.20)

cat("Mean bias:           ", round(mean_bias, 4), "\n")
cat("Trimmed mean (10%):  ", round(trimmed_bias_10, 4), "\n")
cat("Trimmed mean (20%):  ", round(trimmed_bias_20, 4), "\n")
cat("Median bias:         ", round(median_bias, 4), "\n")

# Generate submission with 10% trimmed mean
submission_ets_trimmed10 <- sub_template %>%
  mutate(load = as.numeric(fc_ets_final$mean) + trimmed_bias_10)

write.csv(submission_ets_trimmed10, 
          "output/submission_ets_trimmed10.csv", row.names = FALSE)

head(submission_ets_trimmed10)
```

```{r, eval=FALSE, include=FALSE}
#  ETS with explicit weekly seasonality tuning  

fit_ets_AAA <- ets(train_ts, model = "AAA")
fc_ets_AAA <- forecast(fit_ets_AAA, h = nrow(valid_data))
print(accuracy(fc_ets_AAA, valid_data$load_daily))

fit_ets_AAdA <- ets(train_ts, model = "AAA", damped = TRUE)
fc_ets_AAdA <- forecast(fit_ets_AAdA, h = nrow(valid_data))
print(accuracy(fc_ets_AAdA, valid_data$load_daily))

mape_AAA  <- accuracy(fc_ets_AAA,  valid_data$load_daily)["Test set","MAPE"]
mape_AAdA <- accuracy(fc_ets_AAdA, valid_data$load_daily)["Test set","MAPE"]

if (mape_AAdA < mape_AAA) {
  cat("Winner: AAdA (damped)\n")
  fit_final <- ets(full_ts, model = "AAA", damped = TRUE)
} else {
  cat("Winner: AAA\n")
  fit_final <- ets(full_ts, model = "AAA")
}

fc_final <- forecast(fit_final, h = nrow(sub_template))

submission_ets_tuned <- sub_template %>%
  mutate(load = as.numeric(fc_final$mean))

write.csv(submission_ets_tuned, "submission_ets_tuned.csv", row.names = FALSE)
```

```{r, eval=FALSE, include=FALSE}
#  ETS on log-transformed data  
# log transform
train_ts_log <- ts(log(train_data$load_daily), frequency = 7)
full_ts_log  <- ts(log(full_data$load_daily), frequency = 7)

# training on log scale
fit_ets_log <- ets(train_ts_log)
fc_ets_log <- forecast(fit_ets_log, h = nrow(valid_data))

fc_ets_log_mean <- exp(as.numeric(fc_ets_log$mean))

# accuracy
print(fit_ets_log)   
cat("MAPE:",
    mean(abs(fc_ets_log_mean - valid_data$load_daily) / valid_data$load_daily) * 100,
    "\n")

# plot
validation_results_ets_log <- data.frame(
  date = valid_data$date,
  actual = valid_data$load_daily,
  forecast = fc_ets_log_mean
)

ggplot(validation_results_ets_log, aes(x = date)) +
  geom_line(aes(y = actual, color = "Actual"), linewidth = 1) +
  geom_line(aes(y = forecast, color = "ETS-log"), linewidth = 1) +
  labs(title = "ETS on log-transformed data", x = "Date", y = "Daily Load", color = "") +
  theme_minimal()

# final forecast  
fit_ets_log_final <- ets(full_ts_log)
fc_ets_log_final <- forecast(fit_ets_log_final, h = nrow(sub_template))

submission_ets_log <- sub_template %>%
  mutate(load = exp(as.numeric(fc_ets_log_final$mean)))

write.csv(submission_ets_log, "submission_ets_log.csv", row.names = FALSE)
```

```{r, eval=FALSE, include=FALSE}
# ETS trained on recent 3 years only 

train_data_recent <- train_data %>%
  filter(date >= as.Date("2008-07-01"))

full_data_recent <- full_data %>%
  filter(date >= as.Date("2008-07-01"))

train_ts_recent <- ts(train_data_recent$load_daily, frequency = 7)
full_ts_recent  <- ts(full_data_recent$load_daily, frequency = 7)
fit_ets_recent <- ets(train_ts_recent)
fc_ets_recent <- forecast(fit_ets_recent, h = nrow(valid_data))

print(fit_ets_recent)
print(accuracy(fc_ets_recent, valid_data$load_daily))

fit_ets_recent_final <- ets(full_ts_recent)
fc_ets_recent_final <- forecast(fit_ets_recent_final, h = nrow(sub_template))

submission_ets_recent <- sub_template %>%
  mutate(load = as.numeric(fc_ets_recent_final$mean))

write.csv(submission_ets_recent, "submission_ets_recent.csv", row.names = FALSE)
```

```{r, eval=FALSE, include=FALSE}
#  Ensemble of Top 2 (ETS + TBATS) 
sub_ets   <- read.csv("submission_ets.csv")
sub_tbats <- read.csv("submission_tbats.csv")

submission_ens_top2 <- sub_template %>%
  mutate(load = (sub_ets$load + sub_tbats$load) / 2)

write.csv(submission_ens_top2, "submission_ens_top2.csv", row.names = FALSE)
```

```{r, eval=FALSE, include=FALSE}
### Some Analysis based on bias pattern:

library(lubridate)

# Recompute validation residuals (actual - forecast)
fit_ets_diag <- ets(train_ts)
fc_ets_diag  <- forecast(fit_ets_diag, h = nrow(valid_data))

residuals_df <- data.frame(
  date = valid_data$date,
  actual = valid_data$load_daily,
  forecast = as.numeric(fc_ets_diag$mean),
  residual = valid_data$load_daily - as.numeric(fc_ets_diag$mean),
  weekday = wday(valid_data$date, label = TRUE),
  day_of_month = day(valid_data$date)
)

# 1. Overall bias stats
cat("=== Overall bias ===\n")
cat("Mean bias:    ", round(mean(residuals_df$residual), 4), "\n")
cat("Median bias:  ", round(median(residuals_df$residual), 4), "\n")
cat("SD of bias:   ", round(sd(residuals_df$residual), 4), "\n\n")

# 2. Bias by weekday
cat("=== Bias by weekday ===\n")
weekday_bias <- residuals_df %>%
  group_by(weekday) %>%
  summarise(
    mean_bias = round(mean(residual), 4),
    n = n()
  )
print(weekday_bias)

# 3. Bias trend over time  
cat("\n=== Bias by week-of-month ===\n")
residuals_df$week_of_month <- ceiling(residuals_df$day_of_month / 7)
weekly_bias <- residuals_df %>%
  group_by(week_of_month) %>%
  summarise(
    mean_bias = round(mean(residual), 4),
    n = n()
  )
print(weekly_bias)

# 4. Visualize residuals over time
ggplot(residuals_df, aes(x = date, y = residual)) +
  geom_line(color = "steelblue") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  geom_hline(yintercept = mean(residuals_df$residual),
             linetype = "dashed", color = "darkgreen") +
  labs(title = "ETS Residuals on Validation (July 2010)",
       subtitle = "Red = zero, Green = mean bias",
       x = "Date", y = "Residual (Actual - Forecast)") +
  theme_minimal()
```

```{r, eval=FALSE, include=FALSE}
# ARIMA(+Weather) Model Training  
train_xreg <- train_data_load_temp$temp_daily
valid_xreg <- valid_data_load_temp$temp_daily

fit_arima_temp <- auto.arima(train_msts_load_temp, xreg = train_xreg, seasonal=FALSE)
fc_arima_temp <- forecast(fit_arima_temp, xreg = valid_xreg)

# accuracy
ac_arima_temp <- accuracy(fc_arima_temp, valid_data_load_temp$load_daily)

# plot actual vs forecast on validation dates
validation_results_arima <- data.frame(
  date = valid_data_load_temp$date,
  actual = valid_data_load_temp$load_daily,
  forecast = as.numeric(fc_arima_temp$mean)
)

ggplot(validation_results_arima, aes(x = date)) +
  geom_line(aes(y = actual, color = "Actual"), linewidth = 1) +
  geom_line(aes(y = forecast, color = "ARIMA"), linewidth = 1) +
  labs(
    title = "ARIMA: Validation Forecast vs Actual",
    x = "Date",
    y = "Daily Load",
    color = ""
  ) +
  theme_minimal()

print(ac_arima_temp)
```

```{r, eval=FALSE, include=FALSE}
# ARIMA + Fourier Model Training (Grid Search on K) 

K_grid <- list(
  c(1, 1),
  c(2, 2),
  c(1, 3),
  c(2, 3),
  c(3, 3),
  c(2, 5)
)

results_arima_fourier <- data.frame(
  K_weekly = integer(),
  K_yearly = integer(),
  ARIMA_Order = character(),
  Seasonal_Order = character(),
  AICc = numeric(),
  RMSE = numeric(),
  MAE = numeric(),
  MAPE = numeric(),
  stringsAsFactors = FALSE
)

best_fit_arima_fourier <- NULL
best_fc_arima_fourier <- NULL
best_K <- NULL
best_mape <- Inf

for (K in K_grid) {
  
  train_fourier <- fourier(train_msts_load, K = K)
  valid_fourier <- fourier(train_msts_load, K = K, h = nrow(valid_data))
  
  fit_arima_fourier <- auto.arima(
    train_data_load$load_daily,
    xreg = train_fourier,
    seasonal = FALSE,
    stepwise = FALSE,
    approximation = FALSE
  )
  
  fc_arima_fourier <- forecast(
    fit_arima_fourier,
    xreg = valid_fourier
  )
  
  acc <- accuracy(fc_arima_fourier, valid_data$load_daily)
  
  current_mape <- acc["Test set", "MAPE"]
  
  results_arima_fourier <- rbind(
    results_arima_fourier,
    data.frame(
      K_weekly = K[1],
      K_yearly = K[2],
      ARIMA_Order = paste0(
        "(",
        fit_arima_fourier$arma[1], ",",
        fit_arima_fourier$arma[6], ",",
        fit_arima_fourier$arma[2], ")"
      ),
      Seasonal_Order = paste0(
        "(",
        fit_arima_fourier$arma[3], ",",
        fit_arima_fourier$arma[7], ",",
        fit_arima_fourier$arma[4], ")"
      ),
      AICc = fit_arima_fourier$aicc,
      RMSE = acc["Test set", "RMSE"],
      MAE  = acc["Test set", "MAE"],
      MAPE = current_mape
    )
  )
  
  if (current_mape < best_mape) {
    best_mape <- current_mape
    best_fit_arima_fourier <- fit_arima_fourier
    best_fc_arima_fourier <- fc_arima_fourier
    best_K <- K
  }
}

# sort by MAPE
results_arima_fourier <- results_arima_fourier %>%
  arrange(MAPE)

# show summary table
print(results_arima_fourier)

# best model summary
cat("Best K:", best_K[1], best_K[2], "\n")
cat("Best validation MAPE:", best_mape, "\n")
print(best_fit_arima_fourier)
```

```{r, eval=FALSE, include=FALSE}
# ARIMA + Fourier Model Forecast (Best K) 

full_fourier <- fourier(full_msts_load, K = best_K)
future_fourier <- fourier(full_msts_load, K = best_K, h = nrow(sub_template))

fit_arima_fourier_final <- auto.arima(
  full_data_load$load_daily,
  xreg = full_fourier,
  seasonal = FALSE,
  stepwise = FALSE,
  approximation = FALSE
)

fc_arima_fourier_final <- forecast(
  fit_arima_fourier_final,
  xreg = future_fourier
)

submission_arima_fourier <- sub_template %>%
  mutate(load = as.numeric(fc_arima_fourier_final$mean))

write.csv(
  submission_arima_fourier,
  "submission_arima_fourier_bestK.csv",
  row.names = FALSE
)
```

```{r, eval=FALSE, include=FALSE}
#  ARIMA + Fourier Model Training 
K <- c(2, 2)

train_fourier <- fourier(train_msts_load, K = K)
valid_fourier <- fourier(train_msts_load, K = K, h = nrow(valid_data))

fit_arima_fourier <- auto.arima(
  train_data$load_daily,
  xreg = train_fourier,
  seasonal = FALSE,
  stepwise = FALSE,
  approximation = FALSE
)

fc_arima_fourier <- forecast(
  fit_arima_fourier,
  xreg = valid_fourier
)

# accuracy
ac_arima_fourier <- accuracy(fc_arima_fourier, valid_data$load_daily)
print(ac_arima_fourier)

# plot actual vs forecast
validation_results_arima_fourier <- data.frame(
  date = valid_data$date,
  actual = valid_data$load_daily,
  forecast = as.numeric(fc_arima_fourier$mean)
)

ggplot(validation_results_arima_fourier, aes(x = date)) +
  geom_line(aes(y = actual, color = "Actual"), linewidth = 1) +
  geom_line(aes(y = forecast, color = "Forecast"), linewidth = 1) +
  labs(
    title = "Fourier + ARIMA: Validation Forecast vs Actual",
    x = "Date",
    y = "Daily Load",
    color = ""
  ) +
  theme_minimal()
```

```{r, eval=FALSE, include=FALSE}
# ARIMA + Fourier Model Forecast  
K <- c(2, 2)

full_fourier <- fourier(full_msts_load, K = K)
future_fourier <- fourier(full_msts_load, K = K, h = nrow(sub_template))

fit_arima_fourier_final <- auto.arima(
  full_data_load$load_daily,
  xreg = full_fourier,
  seasonal = FALSE,
  stepwise = FALSE,
  approximation = FALSE
)

fc_arima_fourier_final <- forecast(
  fit_arima_fourier_final,
  xreg = future_fourier
)

submission_arima_fourier <- sub_template %>%
  mutate(load = as.numeric(fc_arima_fourier_final$mean))

write.csv(
  submission_arima_fourier,
  "submission_arima_fourier.csv",
  row.names = FALSE
)
```

```{r, eval=FALSE, include=FALSE}
# ARIMA + Fourier Model Training  
train_data_sq <- train_data %>%
  mutate(temp_sq = temp_daily^2)

valid_data_sq <- valid_data %>%
  mutate(temp_sq = temp_daily^2)

train_msts_sq <- msts(
  train_data_sq$load_daily,
  seasonal.periods = c(7, 365.25)
)

K <- c(2, 2)

train_fourier <- fourier(train_msts_sq, K = K)
valid_fourier <- fourier(train_msts_sq, K = K, h = nrow(valid_data_sq))

train_xreg <- cbind(
  train_fourier,
  temp_daily = train_data_sq$temp_daily,
  temp_sq    = train_data_sq$temp_sq,
  rh_daily   = train_data_sq$rh_daily
)

valid_xreg <- cbind(
  valid_fourier,
  temp_daily = valid_data_sq$temp_daily,
  temp_sq    = valid_data_sq$temp_sq,
  rh_daily   = valid_data_sq$rh_daily
)

fit_arima_weather <- auto.arima(
  train_data_sq$load_daily,
  xreg = train_xreg,
  seasonal = FALSE,
  stepwise = FALSE,
  approximation = FALSE
)

fc_arima_weather <- forecast(
  fit_arima_weather,
  xreg = valid_xreg
)

# accuracy
ac_arima_weather <- accuracy(fc_arima_weather, valid_data_sq$load_daily)
print(ac_arima_weather)

# plot actual vs forecast on validation dates
validation_results_arima <- data.frame(
  date = valid_data_sq$date,
  actual = valid_data_sq$load_daily,
  forecast = as.numeric(fc_arima_weather$mean)
)

ggplot(validation_results_arima, aes(x = date)) +
  geom_line(aes(y = actual, color = "Actual"), linewidth = 1) +
  geom_line(aes(y = forecast, color = "Forecast"), linewidth = 1) +
  labs(
    title = "Fourier + ARIMA + Temperature + Humidity",
    x = "Date",
    y = "Daily Load",
    color = ""
  ) +
  theme_minimal()
```

```{r, eval=FALSE, include=FALSE}
# ARIMA + Fourier Model Forecast 
full_data_sq <- full_data %>%
  mutate(temp_sq = temp_daily^2)

full_msts_sq <- msts(
  full_data_sq$load_daily,
  seasonal.periods = c(7, 365.25)
)

K <- c(2, 2)

full_fourier <- fourier(full_msts_sq, K = K)
future_fourier <- fourier(full_msts_sq, K = K, h = nrow(sub_template))

full_xreg <- cbind(
  full_fourier,
  temp_daily = full_data_sq$temp_daily,
  temp_sq    = full_data_sq$temp_sq,
  rh_daily   = full_data_sq$rh_daily
)

# temperature forecast 
temp_ts <- msts(full_data$temp_daily, seasonal.periods = c(7, 365.25))
fit_temp <- auto.arima(temp_ts, seasonal = FALSE)
fc_temp <- forecast(fit_temp, h = nrow(sub_template))

# humidiy forecast 
rh_ts <- msts(full_data$rh_daily, seasonal.periods = c(7, 365.25))
fit_rh <- auto.arima(rh_ts, seasonal = FALSE)
fc_rh <- forecast(fit_rh, h = nrow(sub_template))

# future xreg 
future_xreg <- cbind(
  future_fourier,
  temp_daily = as.numeric(fc_temp$mean),
  temp_sq    = as.numeric(fc_temp$mean)^2,
  rh_daily   = as.numeric(fc_rh$mean)
)

fit_arima_fourier_weather <- auto.arima(
  full_data_sq$load_daily,
  xreg = full_xreg,
  seasonal = FALSE,
  stepwise = FALSE,
  approximation = FALSE
)

fc_arima_fourier_weather <- forecast(
  fit_arima_fourier_weather,
  xreg = future_xreg
)

# create final submission file
submission_arima_fourier_weather <- sub_template %>%
  mutate(load = as.numeric(fc_arima_fourier_weather$mean))

write.csv(
  submission_arima_fourier_weather,
  "submission_arima_fourier_weather.csv",
  row.names = FALSE
)
```

```{r, eval=FALSE, include=FALSE}
# Neural Network (NNAR) + Fourier  

set.seed(797)   

K_nn <- c(2, 6)  

# training
train_fourier_nn <- fourier(train_msts_load, K = K_nn)
valid_fourier_nn <- fourier(train_msts_load, K = K_nn, h = nrow(valid_data))

fit_nnar <- nnetar(
  train_msts_load,
  p = 2, P = 1,
  xreg = train_fourier_nn
)

fc_nnar <- forecast(fit_nnar, xreg = valid_fourier_nn, h = nrow(valid_data))

ac_nnar <- accuracy(fc_nnar, valid_data$load_daily)
print(ac_nnar)

# plot
validation_results_nnar <- data.frame(
  date = valid_data$date,
  actual = valid_data$load_daily,
  forecast = as.numeric(fc_nnar$mean)
)

ggplot(validation_results_nnar, aes(x = date)) +
  geom_line(aes(y = actual, color = "Actual"), linewidth = 1) +
  geom_line(aes(y = forecast, color = "NNAR"), linewidth = 1) +
  labs(title = "NNAR + Fourier: Validation vs Actual",
       x = "Date", y = "Daily Load", color = "") +
  theme_minimal()

#  final forecast 
set.seed(797)
full_fourier_nn   <- fourier(full_msts_load, K = K_nn)
future_fourier_nn <- fourier(full_msts_load, K = K_nn, h = nrow(sub_template))

fit_nnar_final <- nnetar(
  full_msts_load,
  p = 2, P = 1,
  xreg = full_fourier_nn
)

fc_nnar_final <- forecast(fit_nnar_final,
                          xreg = future_fourier_nn,
                          h = nrow(sub_template))

submission_nnar <- sub_template %>%
  mutate(load = as.numeric(fc_nnar_final$mean))

write.csv(submission_nnar, "submission_nnar_fourier.csv", row.names = FALSE)
```

```{r, eval=FALSE, include=FALSE}
# ARIMA + Fourier with Extended K Grid  

K_grid_ext <- list(
  c(2, 6),
  c(3, 6),
  c(2, 8),
  c(3, 8),
  c(2, 10),
  c(3, 10),
  c(2, 12)
)

results_ext <- data.frame()
best_mape_ext <- Inf
best_K_ext <- NULL

for (K in K_grid_ext) {
  
  train_f <- fourier(train_msts_load, K = K)
  valid_f <- fourier(train_msts_load, K = K, h = nrow(valid_data))
  
  fit_tmp <- auto.arima(train_data_load$load_daily,
                        xreg = train_f,
                        seasonal = FALSE,
                        stepwise = TRUE,       # faster
                        approximation = TRUE)
  
  fc_tmp <- forecast(fit_tmp, xreg = valid_f)
  acc_tmp <- accuracy(fc_tmp, valid_data$load_daily)
  
  results_ext <- rbind(results_ext, data.frame(
    K_weekly = K[1],
    K_yearly = K[2],
    AICc = fit_tmp$aicc,
    MAPE = acc_tmp["Test set", "MAPE"],
    RMSE = acc_tmp["Test set", "RMSE"]
  ))
  
  if (acc_tmp["Test set", "MAPE"] < best_mape_ext) {
    best_mape_ext <- acc_tmp["Test set", "MAPE"]
    best_K_ext <- K
  }
}

results_ext <- results_ext %>% arrange(MAPE)
print(results_ext)
cat("Best K (extended):", best_K_ext[1], best_K_ext[2],
    " | Validation MAPE:", best_mape_ext, "\n")

# final forecast with best K  
full_f_ext   <- fourier(full_msts_load, K = best_K_ext)
future_f_ext <- fourier(full_msts_load, K = best_K_ext, h = nrow(sub_template))

fit_ext_final <- auto.arima(full_data_load$load_daily,
                            xreg = full_f_ext,
                            seasonal = FALSE,
                            stepwise = FALSE,
                            approximation = FALSE)

fc_ext_final <- forecast(fit_ext_final, xreg = future_f_ext)

submission_arima_fourier_extK <- sub_template %>%
  mutate(load = as.numeric(fc_ext_final$mean))

write.csv(submission_arima_fourier_extK,
          "submission_arima_fourier_extK.csv",
          row.names = FALSE)
```

```{r, eval=FALSE, include=FALSE}
#  STLF + ARIMA

# training
fit_stlf <- stlf(train_msts_load,
                 h = nrow(valid_data),
                 method = "arima",
                 s.window = "periodic",
                 robust = TRUE)

ac_stlf <- accuracy(fit_stlf, valid_data$load_daily)
print(ac_stlf)

# plot
validation_results_stlf <- data.frame(
  date = valid_data$date,
  actual = valid_data$load_daily,
  forecast = as.numeric(fit_stlf$mean)
)

ggplot(validation_results_stlf, aes(x = date)) +
  geom_line(aes(y = actual, color = "Actual"), linewidth = 1) +
  geom_line(aes(y = forecast, color = "STLF+ARIMA"), linewidth = 1) +
  labs(title = "STLF + ARIMA: Validation vs Actual",
       x = "Date", y = "Daily Load", color = "") +
  theme_minimal()

#   final forecast 
fit_stlf_final <- stlf(full_msts_load,
                       h = nrow(sub_template),
                       method = "arima",
                       s.window = "periodic",
                       robust = TRUE)

submission_stlf <- sub_template %>%
  mutate(load = as.numeric(fit_stlf_final$mean))

write.csv(submission_stlf, "submission_stlf_arima.csv", row.names = FALSE)
```

```{r, eval=FALSE, include=FALSE}
# Ensemble (Simple Average) 
sub_tbats         <- read.csv("submission_tbats.csv")
sub_arima_fourier <- read.csv("submission_arima_fourier.csv")
sub_nnar          <- read.csv("submission_nnar_fourier.csv")
sub_stlf          <- read.csv("submission_stlf_arima.csv")

# simple average of 4 models
submission_ensemble_avg <- sub_template %>%
  mutate(load = (sub_tbats$load +
                 sub_arima_fourier$load +
                 sub_nnar$load +
                 sub_stlf$load) / 4)

write.csv(submission_ensemble_avg,
          "submission_ensemble_avg.csv",
          row.names = FALSE)

head(submission_ensemble_avg)
```

```{r, eval=FALSE, include=FALSE}
# Ensemble (Weighted by Validation MAPE)
 
mape_tbats         <- accuracy(fc_tbats, valid_data$load_daily)["Test set", "MAPE"]
mape_arima_fourier <- accuracy(fc_arima_fourier, valid_data$load_daily)["Test set", "MAPE"]
mape_nnar          <- accuracy(fc_nnar, valid_data$load_daily)["Test set", "MAPE"]
mape_stlf          <- accuracy(fit_stlf, valid_data$load_daily)["Test set", "MAPE"]

cat("TBATS         MAPE:", round(mape_tbats, 4), "\n")
cat("ARIMA+Fourier MAPE:", round(mape_arima_fourier, 4), "\n")
cat("NNAR          MAPE:", round(mape_nnar, 4), "\n")
cat("STLF          MAPE:", round(mape_stlf, 4), "\n")

inv <- 1 / c(mape_tbats, mape_arima_fourier, mape_nnar, mape_stlf)
w <- inv / sum(inv)
names(w) <- c("TBATS", "ARIMA_Fourier", "NNAR", "STLF")
print(round(w, 3))

submission_ensemble_w <- sub_template %>%
  mutate(load = w["TBATS"]         * sub_tbats$load +
                w["ARIMA_Fourier"] * sub_arima_fourier$load +
                w["NNAR"]          * sub_nnar$load +
                w["STLF"]          * sub_stlf$load)

write.csv(submission_ensemble_w,
          "submission_ensemble_weighted.csv",
          row.names = FALSE)

head(submission_ensemble_w)
```

```{r, eval=FALSE, include=FALSE}
# STLF + ETS  

fit_stlf_ets <- stlf(train_msts_load,
                     h = nrow(valid_data),
                     method = "ets",
                     s.window = "periodic",
                     robust = TRUE)

ac_stlf_ets <- accuracy(fit_stlf_ets, valid_data$load_daily)
print(ac_stlf_ets)

# final forecast
fit_stlf_ets_final <- stlf(full_msts_load,
                           h = nrow(sub_template),
                           method = "ets",
                           s.window = "periodic",
                           robust = TRUE)

submission_stlf_ets <- sub_template %>%
  mutate(load = as.numeric(fit_stlf_ets_final$mean))

write.csv(submission_stlf_ets, "submission_stlf_ets.csv", row.names = FALSE)
```

# AI Usage

Generative AI tools (ChatGPT) were used to assist with code organization, debugging, and improving the clarity of written explanations. 

Specifically, AI was used to refine R code structure, resolve errors related to file paths and LaTeX compilation, and enhance the presentation of results in a more professional format. 

All modeling decisions, including model selection, bias correction methods, and evaluation strategies, were independently developed and verified by the authors.
